Some forms of uncertainty may suppress the evolution of social learning

### 2022-04-21 ms.tex
updated plots with 100 trials and corrected analysis

\begin{itemize}
  \item 
    To understand how different forms of uncertainty affect social learning evolution
    we systematically varied environmental variables in our model and observed
    corresponding changes in mean social learning prevalence, $\meansl$. We
    confirmed that, in many cases, increased environmental variability $u$ 
    suppresses social learning. However\ldots

  \item 
    Our analysis confirmed existing theoretical predictions that social learning
    is valuable only when environments are sufficiently stable, i.e., 
    environmental variability $u$ is sufficiently small.
    Because of the central role of $u$, it is set on the x-axis in
    all analysis plots shown in Figure~\ref{fig:results}. 
    The threshold over $u$ at which social learning begins to decline
    varies depending on the value of other environmental parameters.

  \item 
    However, more possible behaviors $B$ ($B=2,4,10$ for the first, second, and
    third column respectively in Figure~\ref{fig:results}) can lead
    social learning to be selected for even for large values of $u$, possibly
    due to the low risk and potentially high reward of learning an accurate
    tally of mean payoffs from the previous generation. 
    Since there are many behaviors and
    few observations, softmax weighting will not significantly 
    favor a sub-optimal behavior. However, if one does learn an accurate tally
    then one does have an increased chance of performing the best one.

  \item 
    $\pilow$ can alter selection selection pressure for or
    against social learning, depending on the number of time steps per generation.
    For instance, when $B=2$, increasing $\pilow$ (i.e. increased uncertainty
    about which behavior is optimal) leads at first to less sharp sigmoid curve, 
    where social learning is less prevalent with increased $\pilow$ when
    $u < 0.5$ and social learning is more prevalent with increased $\pilow$
    when $u > 0.5$. When $\pilow = 0.8$ noise and genetic drift dominate across
    tested values of $B$, with possibly a slight inverse correlation 
    in social learning as $u$ increases. When $B \in \{4,10\}$, increasing
    $\pilow \in \{0.1, 0.5\}$ leads uniformly to increased $\meansl$ over 
    $u$ in those settings.

  \item
    If $M/B$ has an effect it is mostly to 
    increase reliance on social learning due to social information being of 
    higher quality since teachers would have had more learning opportunities
    for larger $M$. (THERE ARE CASES WHERE THIS IS NOT THE CASE BUT THERE IS 
    STILL TOO MUCH NOISE DUE TO SMALL NTRIALS)

  \item
    Synthesis/analysis conclusion

\end{itemize}

>>>>

% \begin{itemize}
%   \item 
%     To understand how different forms of uncertainty affect social learning evolution
%     we systematically varied environmental variables in our model and observed
%     corresponding changes in mean social learning prevalence, $\meansl$. We
%     confirmed that, in many cases, increased environmental variability $u$ 
%     suppresses social learning. However\ldots

%   \item 
%     Our analysis confirmed existing theoretical predictions that social learning
%     is valuable only when environments are sufficiently stable, i.e., 
%     environmental variability $u$ is sufficiently small.
%     Because of the central role of $u$, it is set on the x-axis in
%     all analysis plots shown in Figure~\ref{fig:results}. 
%     The threshold over $u$ at which social learning begins to decline
%     varies depending on the value of other environmental parameters.

%   \item 
%     However, more possible behaviors $B$ ($B=2,4,10$ for the first, second, and
%     third column respectively in Figure~\ref{fig:results}) can lead
%     social learning to be selected for even for large values of $u$, possibly
%     due to the low risk and potentially high reward of learning an accurate
%     tally of mean payoffs from the previous generation. 
%     Since there are many behaviors and
%     few observations, softmax weighting will not significantly 
%     favor a sub-optimal behavior. However, if one does learn an accurate tally
%     then one does have an increased chance of performing the best one.

%   \item 
%     $\pilow$ can alter selection selection pressure for or
%     against social learning, depending on the number of time steps per generation.
%     For instance, when $B=2$, increasing $\pilow$ (i.e. increased uncertainty
%     about which behavior is optimal) leads at first to less sharp sigmoid curve, 
%     where social learning is less prevalent with increased $\pilow$ when
%     $u < 0.5$ and social learning is more prevalent with increased $\pilow$
%     when $u > 0.5$. When $\pilow = 0.8$ noise and genetic drift dominate across
%     tested values of $B$, with possibly a slight inverse correlation 
%     in social learning as $u$ increases. When $B \in \{4,10\}$, increasing
%     $\pilow \in \{0.1, 0.5\}$ leads uniformly to increased $\meansl$ over 
%     $u$ in those settings.

%   \item
%     If $M/B$ has an effect it is mostly to 
%     increase reliance on social learning due to social information being of 
%     higher quality since teachers would have had more learning opportunities
%     for larger $M$. (THERE ARE CASES WHERE THIS IS NOT THE CASE BUT THERE IS 
%     STILL TOO MUCH NOISE DUE TO SMALL NTRIALS)

%   \item
%     Synthesis/analysis conclusion

% \end{itemize}
